The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-09-10 paper/ms.tex
redid gaia match more rigorously

Amongst our sample are pulsating stars of spectral type~B,~A, and~F, with their names, properties and variability class listed in Table~\ref{all_stars}. The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18}. These studies cover about 70 stars so far. However, the vast majority of intermediate-mass stars observed by Kepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties. One of the valuable outputs of our current work includes the reduced light curves of several early-B stars, which were only scarcely targeted in the nominal \kepler mission. The few that were monitored did not reveal suitable oscillation frequency patterns to achieve a unique mode identification, which is a requirement to perform asteroseismic modelling. The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown, yet they play a pivotal role in stellar and galactic evolution. The in-depth asteroseismic analysis of the smear data for the~B~stars in this work is beyond the scope of the current paper, as it requires additional ground-based follow-up spectroscopy. Such studies will be the subject of future work.

@@

Several stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect. \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. A detailed study of these stars will be presented by Antoci et al., in prep.

>>>>

Amongst our sample are pulsating stars of spectral type~B,~A, and~F, with their names, properties and variability class listed in Table~\ref{all_stars}.

Several stars have a more complex classification than can be adequately noted in Table~\ref{all_stars}: HD~189684 is listed as an ellipsoidal variable, but also shows evidence for $\gamma$\,Dor variability. HD~185397 and HD~186255 are listed as $\gamma$\,Dor/$\delta$\,Sct hybrids, but may in fact simply be $\delta$\,Sct variables with nonlinear combination frequencies, and a detailed frequency analysis will be required to distinguish between these possibilities. HD~184788 shows acombination of two rotational modulation signals with base frequencies: 0.0885 and~$0.1966 c/d$. HD~184875 is a $\gamma$\,Dor but also shows evidence for an unknown contaminant. V554~Lyr and V2079~Cyg are both known $\alpha^2$\,CVn variables, and the latter also shows a weak $\delta$\,Sct signal. The detection of rotational modulation in the chemically-peculiar HD~175132 suggests its reclassification as an $\alpha^2$\,CVn variable.

The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18}. These studies cover about 70 stars so far. However, the vast majority of intermediate-mass stars observed by Kepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties. One of the valuable outputs of our current work includes the reduced light curves of several early-B stars, which were only scarcely targeted in the nominal \kepler mission. The few that were monitored did not reveal suitable oscillation frequency patterns to achieve a unique mode identification, which is a requirement to perform asteroseismic modelling. The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown, yet they play a pivotal role in stellar and galactic evolution. The in-depth asteroseismic analysis of the smear data for the~B~stars in this work is beyond the scope of the current paper, as it requires additional ground-based follow-up spectroscopy. Such studies will be the subject of future work.

@@

Several stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect. The identification for HD~189178 is tentative, as the spectrum also resembles that of an SPB star, while for HD~184787 there is long term variability consistent with contamination. The other hump-and-spike identifications seem secure. \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. A detailed study of these stars will be presented by Antoci et al., in prep.
